FLM for growth as function of SPEI

### 2021-02-17 analysis/paper/vital rate models.Rmd
plotted difference between two crossbasis smooths.

```{r}
breaks <- seq(0,36, by = 2)
ggplot(s_1ha_eval, aes(y = spei_history, x = L, fill = est, z = est)) +
  geom_raster() +
  geom_contour(color = "black", binwidth = 0.002) +
  scale_fill_viridis_c("P(survival)", option = "magma", limits = surv_lims) +
  scale_x_reverse(
    "lag (months)",
    breaks = breaks,
    expand = c(0, 0),
    labels = function(x) -x,
    sec.axis = dup_axis(name = "month",
                        labels = month(ymd("2020-2-01") - months(breaks), label = TRUE))
  )+
  scale_y_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  # labs(title = "1ha fragments") +
  theme_bw() +
  theme(axis.text.x.top = element_text(angle = 45, vjust = 0.2, hjust = 0)) +
  NULL
```

>>>>

```{r}
breaks <- seq(0,36, by = 2)
s_1ha_rotated <-
  ggplot(s_1ha_eval, aes(y = spei_history, x = L, fill = est, z = est)) +
  geom_raster() +
  geom_contour(color = "black", binwidth = 0.002) +
  scale_fill_viridis_c("P(survival)", option = "magma", limits = surv_lims) +
  scale_x_reverse(
    "lag (months)",
    breaks = breaks,
    expand = c(0, 0),
    labels = function(x) -x,
    sec.axis = dup_axis(name = "month",
                        labels = month(ymd("2020-2-01") - months(breaks), label = TRUE))
  )+
  scale_y_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  labs(title = "1ha fragments") +
  theme_bw() +
  theme(axis.text.x.top = element_text(angle = 45, vjust = 0.2, hjust = 0)) +
  NULL
```
```{r}
s_cf_rotated <- 
  ggplot(s_cf_eval, aes(y = spei_history, x = L, fill = est, z = est)) +
  geom_raster() +
  geom_contour(color = "black", binwidth = 0.002) +
  scale_fill_viridis_c("P(survival)", option = "magma", limits = surv_lims) +
  scale_x_reverse(
    "lag (months)",
    breaks = breaks,
    expand = c(0, 0),
    labels = function(x) -x,
    sec.axis = dup_axis(name = "month",
                        labels = month(ymd("2020-2-01") - months(breaks), label = TRUE))
  )+
  scale_y_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  labs(title = "Continuous Forest") +
  theme_bw() +
  theme(axis.text.x.top = element_text(angle = 45, vjust = 0.2, hjust = 0)) +
  NULL
```

Try plotting a raster of the difference between CF and 1-ha

```{r}
s_diff_rotated <- 
  bind_cols(
  s_cf_eval %>% rename_with(.fn = ~glue("cf_{.}")),
  s_1ha_eval %>% rename_with(.fn = ~glue("frag_{.}"))
  ) %>%
  mutate(diff = cf_est - frag_est) %>% 
  ggplot(aes(x = cf_L, y = cf_spei_history, fill = diff, z = diff)) +
  geom_raster() +
  geom_contour(color = "black", binwidth = 0.002) +
  scale_fill_viridis_c("∆Survival (CF – 1ha)", option = "plasma") +
  scale_x_reverse(
    "lag (months)",
    breaks = breaks,
    expand = c(0, 0),
    labels = function(x) -x,
    sec.axis = dup_axis(name = "month",
                        labels = month(ymd("2020-2-01") - months(breaks), label = TRUE))
  )+
  scale_y_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  labs(title = "CF – 1-ha") +
  theme_bw() +
  theme(axis.text.x.top = element_text(angle = 45, vjust = 0.2, hjust = 0)) +
  NULL
```
```{r}
(s_cf_rotated |s_1ha_rotated) / (s_diff_rotated | plot_spacer()) + plot_layout(guides="collect")
```
